A meta-analysis of mental rotation ability in the first years of life

### 2022-04-30 code/analysis.Rmd
Improve Bayesian models
- Use non-centered intercept, which doesn't change the results but
samples better

- Use `bayestestR` to summarize the posterior distribution (incl. Bayes
factors)

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)
library(tidybayes)
library(cowplot)

@@

```{r, meta_analysis_bayes}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "Intercept"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
res_prior <- brm(
  gi | se(sei) ~ 1 + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 10000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior)
# plot(res_prior)

@@

# Compute probabilities of the meta-analytic being greater than 0
hypothesis(res_brm, "Intercept > 0")$hypothesis

@@

# Compute by-article variance
var_article <- as.matrix(
  res_brm,
  variable = "sd_article__Intercept"
)^2
mean_qi(var_article_draws)

@@

```{r, meta_regression_bayes}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "Intercept"),
  set_prior("normal(0, 0.5)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ gender * age_c + task + (1 | article / experiment),
  data = dat_reg,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 10000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior_reg)
# plot(res_prior_reg)

@@

# Compute probabilities of the different effects being greater than 0
hypothesis(res_brm_reg, "gender3M2 > 0")$hypothesis
hypothesis(res_brm_reg, "gender2M1 < 0")$hypothesis
hypothesis(res_brm_reg, "task2M1 > 0")$hypothesis

>>>>

```{r, setup, include=FALSE}
# Load packages
library(here)
library(ggridges)
library(tidyverse)
library(magrittr)
library(metafor)
library(brms)
library(bayestestR)
library(tidybayes)
library(cowplot)

@@

```{r, meta_analysis_bayes}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
n_iter <- 20000
res_prior <- brm(
  gi | se(sei) ~ 0 + Intercept + (1 | article / experiment),
  data = dat,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = n_iter,
  warmup = 1000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior)
# plot(res_prior)

@@

# Summarise fixed effects (incl. Bayes factors)
describe_posterior(
  res_brm,
  centrality = "mean", ci = 0.95, ci_method = "ETI",
  test = c("p_direction", "rope", "bayesfactor"),
  rope_range = c(-0.1, 0.1)
)

@@

# Compute by-article variance
var_article <- as.matrix(
  res_brm,
  variable = "sd_article__Intercept"
)^2
mean_qi(var_article)

@@

```{r, meta_regression_bayes}
# Specify priors
prior_c <- c(
  set_prior("normal(0, 1)", class = "b", coef = "Intercept"),
  set_prior("normal(0, 0.5)", class = "b"),
  set_prior("cauchy(0, 0.3)", class = "sd")
)

# Run prior predictive simulation
res_prior_reg <- brm(
  gi | se(sei) ~ 0 + Intercept + gender * age_c + task +
    (1 | article / experiment),
  data = dat_reg,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = n_iter,
  warmup = 1000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior_reg)
# plot(res_prior_reg)

@@

# Summarise fixed effects (incl. Bayes factors)
describe_posterior(
  res_brm_reg,
  centrality = "mean", ci = 0.95, ci_method = "ETI",
  test = c("p_direction", "rope", "bayesfactor"),
  rope_range = c(-0.1, 0.1)
)
